A generalized definition of multidimensional item response theory parameters

### 2023-02-24 output/paper_draft/paper_M2PLM_parameters.Rmd
Updates the notation to consistently refer to the coordinates of the vectors in the latent space referred to a concrete basis

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  cache    = TRUE,
  dev      = "png",
  dpi      =   300,
  dev.args = list(type = "cairo-png"),
  fig.pos = "!H"
)

@@

is independent of whether the inner product is standard or not.
Therefore, to compute the direction cosine $`r DIR_COS_ANY`$
of vector $`r TRAIT_VECTOR`$ along dimension $`r DIM_INDEX`$,
we plug it into Equation \@ref(eq:cos-vectors) along with
the corresponding basis vector $`r BASIS_VECTOR_ANY`$:

@@

Let's consider now the vector $`r DIR_COS_VEC`$, made up by the $`r N_DIMS`$
direction cosines of $`r TRAIT_VECTOR`$ with
the basis vectors of $`r LS_BASIS`$.

@@

To compute the direction of the maximum slope,
Reckase leverages on the property that the squared direction cosines sum up to 1
(see Equation 7 therein).
However, this assertion implicitly assumes orthogonal coordinates,
so it does not apply in general to $`r DIR_COS_VEC`$.
Instead, we may consider the direction cosine vector with the standard basis
$`r LS_STD_BASIS`$.
Now, applying Proposition 2 (with $`r ALT_MATRIX_AS_ID`$) we obtain

>>>>

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  cache    = FALSE,
  dev      = "png",
  dpi      =   300,
  dev.args = list(type = "cairo-png"),
  fig.pos = "!H"
)

@@

is independent of whether the inner product is standard or not.
Therefore, to compute the direction cosine $`r DIR_COS_ANY_ORG`$
of vector $`r TRAIT_VECTOR`$ along dimension $`r DIM_INDEX`$,
we plug it into Equation \@ref(eq:cos-vectors) along with
the corresponding basis vector $`r BASIS_VECTOR_ANY`$:

@@

Let's consider now the vector $`r DIR_COS_VEC_ORG`$, made up by the $`r N_DIMS`$
direction cosines of $`r TRAIT_VECTOR`$ with
the basis vectors of $`r LS_BASIS`$.

@@

To compute the direction of the maximum slope,
Reckase leverages on the property that the squared direction cosines sum up to 1
(see Equation 7 therein).
However, this assertion implicitly assumes orthogonal coordinates,
so it does not apply in general to $`r DIR_COS_VEC_ORG`$.
Instead, we may consider the direction cosine vector with the standard basis
$`r LS_STD_BASIS`$.
Now, applying Proposition 2 (with $`r ALT_MATRIX_AS_ID`$) we obtain
